master thesis

### 2017-10-02 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v2.tex
Foreword deleted, new subtitle, tidy up
Former-commit-id: 64ad677d07144f1eb5b647dde423c8b8a6559879

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}
  	\begin{center}
      {\Large Freie Universität Berlin}\\
    	\begin{Huge}
      	Fachbereich Mathematik und Informatik\\
      	\vspace{3mm}
    	\end{Huge}
    	\vspace{20mm}
    	\begin{Large}
    	    \textbf{Origins and losses of parasitism}\\
          (Likelihood, parsimony and other algorithms for ancectral state reconstruction)\\
    	\end{Large}
    	\vspace{8mm}
      Version 2\\
      2.10.2017\\
    	\vspace{2cm}
    	Lydia Buntrock \\
      E-Mail: info@irallia.de\\
     	\vspace{5cm}
      \textbf{Betreuer:}\\
      Dr. Bernhard Y. Renard\\
      \& \\
      Prof. Dr. rer. nat. Emanuel Heitlinger\\      
  	\end{center}
  	\clearpage
  \end{titlepage}

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Foreword}
  Acknowledgement to those who have helped you. \\
  A foreword (one of the most often misspelled words in the language) is most often written by 
    someone other than the author: an expert in the field, a writer of a similar book, etc. 
    Forewords help the publisher at the level of marketing: An opening statement by an eminent and 
    well-published author gives them added credibility in pitching the book to bookstores. Forewords 
    help the author by putting a stamp of approval on their work.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Preface}
  The Preface must include a statement indicating the student's contribution to the following:
  \begin{itemize}
    \item Identification and design of the research program,
    \item Performance of the various parts of the research, and
    \item Analysis of the research data.
  \end{itemize}
  Certain additional elements may also be required, as specified below.
  \begin{itemize}
    \item If any of the work presented in the thesis has led to any publications or submissions, all 
      of these must be listed in the Preface. Bibliographic details should include the title of the 
      article and the name of the publisher (if the article has been accepted or published), and the 
      chapter(s) of the thesis in which the associated work is located.
    \item If the work includes publications or material submitted for publication, the statement 
      described above must detail the relative contributions of all collaborators and co-authors 
      (including supervisors and members of the supervisory committee) and state the proportion of 
      research and writing conducted by the student. For further details, see “Including Published 
      Material in a Thesis or Dissertation”.
    \item If the work includes other scholarly artifacts (such as film and other audio, visual, and 
      graphic representations, and application-oriented documents such as policy briefs, curricula, 
      business plans, computer and web tools, pages, and applications, etc.), all of these must be 
      listed in the Preface (with bibliographical information, if applicable).
    \item If ethics approval was required for the research, the Preface must name the responsible 
      UBC Research Ethics Board, and report the project title(s) and the Certificate Number(s) of 
      the Ethics Certificate(s) applicable to the project.
  \end{itemize}
  In a thesis where the research was not subject to ethics review, produced no publications, and was 
    designed, carried out, and analyzed by the student alone, the text of the Preface may be very 
    brief. Samples are available on this website and in the University Library's online repository 
    of accepted theses. \\
  The content of the Preface must be verified by the student's supervisor, whose endorsement must 
    appear on the final Thesis/Dissertation Approval form. \\
  Acknowledgements, introductory material, and a list of publications do not belong in the Preface. 
    Please put them respectively in the Acknowledgements section, the first section of the thesis, 
    and the appendices. \\

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
    called “the research question(s)”), and provide sufficient background information to enable a 
    non-specialist scholar to understand them. It must contain a thorough review of relevant 
    literature, perhaps in a separate chapter. \\

@@

  If a preface is about the book as a book, the introduction is about the content of the book. 
    Sometimes it is as simple as that: It introduces what is covered in the book. Other times it 
    introduces by setting the overall themes of the book, or by establishing definitions and 
    methodology that will be used throughout the book. Scholarly writers sometimes use the 
    introduction to tell their profession how the book should be viewed academically (that is, they 
    position the book as a particular approach within a discipline or part of a discipline). This 
    latter material is appropriate for a preface, as well. The point is that it should appear in the 
    preface or the introduction, not both. \\
  I helped authors with the front end of their books in two recent cases by refining for them the 
    differences between these rubrics of foreword, preface, and introduction. Because these books 
    were very practical books, I also introduced the rubric of “How to Use This Book.” \\
  Not only did these authors take several stabs at describing their book’s contents via their 
    preface and introduction, they actually tried one more time in their first chapter. \\
  In both cases I set up three rubrics for the front end of the book: Preface, How to Use This Book, 
    and Introduction. I then put like with like. I sorted out the various descriptions of why the 
    book had been written and placing them under the heading “Preface.” I found sentences that dealt 
    with the use of the book and placed them under the heading of “How to Use This Book.” I took the 
    various explanations of what the reader was going to read and placed them under the heading of 
    “Introduction.” I also, in one case, deleted the repeated material in the first chapter, and in 
    the other case, moved the repeated material from the first chapter to the Introduction, 
    replacing a less-well-stated introductory comment there. \\
  In both instances the authors felt that I had waved a magic wand over the material. They felt a 
    sense of satisfaction, knowing that their manuscripts now clearly explained to the reader why 
    they wrote their book, how it was to be used, and the details of what it covered. \\
  What about you and your manuscript? I believe the above definitions and distinctions may alleviate 
    the anxiety you likely feel as a writer. You are anxious to be clear, you want to feel justified 
    in addressing readers with your content, you want to establish your credibility, and you want to 
    set the parameters of your time together. Keep in mind that your anxiety may be what is causing 
    your own confusion at the beginning of a book. If unaddressed, it will cause confusion in your 
    readers. \\
  So just calm down and sort through your material as described above. You may be surprised to find 
    that the exercise does something else for you, revealing a better way for you to construct, or 
    reconstruct, the rest of your manuscript!

>>>>

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}
  	\begin{center}
      {\Large Freie Universität Berlin}\\
    	\begin{Huge}
      	Fachbereich Mathematik und Informatik\\
      	\vspace{3mm}
    	\end{Huge}
    	\vspace{20mm}
    	\begin{Large}
    	    \textbf{Origins and losses of parasitism}\\
          an analysis of the phylogenetic tree of life with a parsimony-like algorithm\\
    	\end{Large}
    	\vspace{8mm}
      Version 2\\
      2.10.2017\\
    	\vspace{2cm}
    	Lydia Buntrock \\
      E-Mail: info@irallia.de\\
     	\vspace{5cm}
      \textbf{Betreuer:}\\
      Dr. Bernhard Y. Renard\\
      \& \\
      Prof. Dr. rer. nat. Emanuel Heitlinger\\      
  	\end{center}
  	\clearpage
  \end{titlepage}

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Preface}
  \todotext{The Preface} must include a statement indicating the student's contribution to the 
    following:
  \begin{itemize}
    \item Identification and design of the research program,
    \item Performance of the various parts of the research, and
    \item Analysis of the research data.
  \end{itemize}
  Certain additional elements may also be required, as specified below.
  \begin{itemize}
    \item If any of the work presented in the thesis has led to any publications or submissions, all 
      of these must be listed in the Preface. Bibliographic details should include the title of the 
      article and the name of the publisher (if the article has been accepted or published), and the 
      chapter(s) of the thesis in which the associated work is located.
    \item If the work includes publications or material submitted for publication, the statement 
      described above must detail the relative contributions of all collaborators and co-authors 
      (including supervisors and members of the supervisory committee) and state the proportion of 
      research and writing conducted by the student. For further details, see “Including Published 
      Material in a Thesis or Dissertation”.
    \item If the work includes other scholarly artifacts (such as film and other audio, visual, and 
      graphic representations, and application-oriented documents such as policy briefs, curricula, 
      business plans, computer and web tools, pages, and applications, etc.), all of these must be 
      listed in the Preface (with bibliographical information, if applicable).
    \item If ethics approval was required for the research, the Preface must name the responsible 
      UBC Research Ethics Board, and report the project title(s) and the Certificate Number(s) of 
      the Ethics Certificate(s) applicable to the project.
  \end{itemize}
  In a thesis where the research was not subject to ethics review, produced no publications, and was 
    designed, carried out, and analyzed by the student alone, the text of the Preface may be very 
    brief. Samples are available on this website and in the University Library's online repository 
    of accepted theses. \\
  The content of the Preface must be verified by the student's supervisor, whose endorsement must 
    appear on the final Thesis/Dissertation Approval form. \\
  Acknowledgements, introductory material, and a list of publications do not belong in the Preface. 
    Please put them respectively in the Acknowledgements section, the first section of the thesis, 
    and the appendices. \\

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  \todotext{A. Introduction.} The thesis must clearly state its theme, hypotheses and/or goals
    (sometimes called “the research question(s)”), and provide sufficient background information to 
    enable a non-specialist scholar to understand them. It must contain a thorough review of 
    relevant literature, perhaps in a separate chapter. \\

@@
